Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finshing section discussing emission measure ratio histograms

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$.

@@

	\par Hydrodynamic loop models, combined with sophisticated forward modeling, provide an accurate method for assessing a wide variety of heating scenarios and calculating observables. Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. 

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated and an intermediate heating frequency of $t_N=2500$ s. The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\par\hl{Discuss usefullness of hot slope versus cool slope via figure; discuss advantages of em ratio; discuss em ratio figures; break into subsections?}

@@

		\caption{Power-law fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}

@@

@@

		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair.\hl{Need a more descriptive caption here!}}

@@

		\caption{Diagnostics figures}

@@

@@

@@

	%%%%%%%%%
	\par As seen in \autoref{fig:histos}, these histograms, denoted by type of slope (i.e. hot or cool) and species, are constructed in one of two ways: each distinct histogram (denoted by linestyle and/or color) is either representative of a distinct heating function (e.g. top row of \autoref{fig:histos}) or a distinct value of $t_N$ (e.g. bottom row of \autoref{fig:histos}). In the four panels of \autoref{fig:histos}, we choose to separate the cool emission measure slopes by type of heating function and the hot emission measure slopes by $t_N$. This means, for example, that the dot-dashed blue $\alpha=-1.5,\beta=1$ histogram in the upper left panel of \autoref{fig:histos} encapsulates cool emission measure slopes for $250\le T_N\le5000$ s while the solid blue $T_N=2000$ s histogram in the lower left panel includes emission measure slopes for all 10 types of heating functions (as listed in \autoref{fig:parameter_space} and the legend in the upper left panel of \autoref{fig:histos}). All histograms are normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$. Additionally, the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}.

@@

>>>>

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $t_N\to0$.

@@

	\par Hydrodynamic loop models, combined with sophisticated forward modeling, provide an accurate method for assessing a wide variety of heating scenarios and calculating observables. Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<t_N<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. 

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated with an intermediate heating frequency of $t_N=2500$ s. The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\subsubsection{Emission Measure Slope}
	\label{subsubsec:em_slope}

@@

		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}

@@

	\par From the left panel of \autoref{fig:em_slope_varying_bounds}, we see that, while $a$ is relatively insensitive to the fit interval, $b$ varies between approximately 2 and 4.5 depending on the choice of bounds of the fit interval. Furthermore, the uncertainty in the fitting procedure for $b$ is relatively large, with the average uncertainty over the entire range of $T_{h,max}$ being $\bar{\sigma}_b\approx0.17$.  Contrastingly, we find that $a\approx2.3$ with little variation over all values of $T_{c,max}$ considered here and that $\bar{\sigma}_a\approx0.018$, nearly an order of magnitude smaller than $\bar{\sigma}_b$. The overlaid fit lines in the right panel of \autoref{fig:em_slope_varying_bounds} similarly show that while $\log{\mathrm{EM}}$ is roughly linear over $5.7<\log{T}<6.5$, this is not the case for the interval $6.7<\log{T}<7.2$. In particular, a function of the form $T^{-b}$ cannot describe the hot shoulder in the emission measure distribution near $10^{7.1}$ K.
	\subsubsection{Emission Measure Ratio}
	\label{subsubsec:em_ratio}
	\par\hl{Lead in with how EM ratio is better, i.e. not masquerading as a fit, just a single point; discussion of results from Brosius, how lines were chosen, then discuss histograms and types.}

@@

		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}. \textbf{Left:} Emission measure ratios separated by heating function type. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, we only show five values of $t_N$.}
		\label{fig:em_ratio_hist_el}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_el}, but for the case where only the ions are heated.}
		\label{fig:em_ratio_hist_ion}

@@

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side. Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma. 

@@

	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$. We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$. It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.

@@

	\par Similarly, we compute this same emission measure ratio for the case in which only the ions are heated. The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function. Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measures ratios is relatively insensitive to $\alpha$. However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$. The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$. With the exception of the $t_N=2000$ s and $t_N=3000 s$ group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}). In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5. In general, the emission measure ratio appears to be more sensitive to $t_N$ compared to the electron heating case.

@@

	\par\hl{Probably cut most of this..}
